News Topic Modeling

### 2017-11-02 paper/R/02_combine.Rmd
new model estimation

### Remove customized stopwords
```{r}
mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")

>>>>

### Remove customized stopwords
```{r}
mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")

### 2017-11-02 paper/R/03_stm.Rmd
new model estimation

@@

## Preliminaries

We load libraries needed for this analysis.

  library(tidytext)    # Tidy text mining
  library(tm)    # Tidy text mining
  library(hunspell)    # Text processing
  library(stringdist)  # String distances
  library(topicmodels) # Topic modelling
  library(proxy)       # Distance measures
  library(SnowballC)   # Stemming
})

@@

```{r caching, echo = FALSE}
load("../output/models/LDAGibbs 40 .Rda")

#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE)

## Pre-processing

### Shaping
```{r}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") ->
  # Assign to variable
  posts_tokenized.dt
```

We remove words that are less than 3 characters long.

```{r Remove short words}

### Filtering and Casting

We summarise the data format into a more compressed form and convert it into a document term matrix.

```{r Term Frequency}

# Summarise
posts_tokenized.dt %>% 
  group_by(articleID, word) %>%
  dplyr::summarise(term_frequency = n()) %>%
  ungroup() ->
  posts_tokenized.dt

```{r Cast to DTM, eval=FALSE, include=FALSE}
# Convert to document term matrix
posts_tokenized.dt %>% 
  cast_dtm(articleID, word, term_frequency) ->
  posts_tokenized.dtm
```

### Topic modelling

#### LDA Training

##### Build Corpus
```{r eval=FALSE, include=FALSE}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw

# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)
# Assign name to docs
rownames(dtm) <- make.unique(btw$title)
```

##### Run LDA using Gibbs sampling

```{r eval=FALSE, include=FALSE}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

```{r eval=FALSE, include=FALSE}
t1 <- Sys.time()
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

Training took 50 minutes on the full dataset. We extract the word-topic probabilities, and the document-topic probabilities produced by the model.

alternatively...
```{r eval=FALSE, include=FALSE}
# Train the LDA model
LDA(
  x       = posts_tokenized.dtm,
  k       = 40,
  method  = "Gibbs",
  control = list(seed = 7292)
) -> posts.lda
```

@@

We take a look at samples of articles labeled with the topics and the most relevant words that use them, and label them according to the prevalent theme. These are recorded in a csv file and loaded in:

@@

  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID) 
```
### Create Topic Labels
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

@@

We extract the top 30 most relevant words and plot them as follows:

  1. Compute the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities and construct a distance matrix,
  2. Apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
  3. Plot each word near the center of the topic mass and repel them from each other.

```{r eval=FALSE, include=FALSE}
posts.wtp %>% 
  # Compute Jensen-Shannon
  computeJensenShannonPCA() %>% {

@@

set.seed(9272)
posts.dtp %>% 
  group_by(title = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw %>% select(title, articleID), by = "title") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>% 
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(10) %>% 
  mutate(row = row_number()) %>% 
  ungroup() ->
  posts_classification.sdt

```{r Document classification chart, eval=FALSE, include=FALSE}

>>>>

  library(tidytext)    # Tidy text mining
  library(tm)    # Tidy text mining
  library(hunspell)    # Text processing
  library(stringdist)  # String distances
  library(topicmodels) # Topic modelling
  library(stm)         # Sructural Topic Model
  library(proxy)       # Distance measures
  library(SnowballC)   # Stemming
})

```{r caching, echo = FALSE}
load("../output/models/LDAGibbs 40 .Rda")
load("../output/models/STM 40 .Rda")
#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE)

@@

![Research Strategy](../figs/research_strategy.png)

## Dataset

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6307 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from six different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the article. We include the month the document was written and the news agency as covariates on topical prevalence. We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.

Figure -- shows the number of articles by news agency and the how many of these articles were shared on Facebook.

```{r echo=FALSE}
btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)

btw %>%
  ggplot(aes(site, fill=shared)) +
  geom_bar(alpha = .7) +
  labs(x="", y="Count") 
```

```{r}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") ->
  # Assign to variable
  posts_tokenized.dt

# Summarise
posts_tokenized.dt %>% 
  group_by(articleID, word) %>%
  dplyr::summarise(term_frequency = n()) %>%
  ungroup() ->
  posts_tokenized.dt
```

### LDA Training

```{r eval=FALSE, include=FALSE}
# Build Corpus
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw

# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)
# Assign name to docs
rownames(dtm) <- make.unique(btw$title)

# ---------- STM ----------- #

btw$month <- month(btw$date)
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","month","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

```{r eval=FALSE, include=FALSE}
## Run LDA using Gibbs sampling

#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

```{r}
t1 <- Sys.time()
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))

# ---------- STM ----------- #

t1 <- Sys.time()
stmOut <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=k, 
           prevalence = ~site+s(month), 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))

@@

@@

@@

  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID) 
```

```{r}
### Create Topic Labels

## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

@@

### Sample articles

To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.

set.seed(9272)
posts.dtp %>% 
  group_by(title = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw %>% select(title, articleID), by = "title") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>% 
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(5, replace = TRUE) %>% 
  mutate(row = row_number()) %>% 
  ungroup() ->
  posts_classification.sdt

```{r Document classification chart, echo=TRUE}

### News landscape

After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label. The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic. It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities. We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.

```{r echo=TRUE}
posts.wtp %>% 
  # Compute Jensen-Shannon
  computeJensenShannonPCA() %>% {

@@

### 2017-11-02 paper/R/03_topic model.Rmd
new model estimation

@@

## Preliminaries

We load libraries needed for this analysis.

  library(tidytext)    # Tidy text mining
  library(tm)    # Tidy text mining
  library(hunspell)    # Text processing
  library(stringdist)  # String distances
  library(topicmodels) # Topic modelling
  library(proxy)       # Distance measures
  library(SnowballC)   # Stemming
})

```{r caching, echo = FALSE}
load("../output/models/LDAGibbs 40 .Rda")

#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE)

## Pre-processing

### Shaping
```{r}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") ->
  # Assign to variable
  posts_tokenized.dt
```

We remove words that are less than 3 characters long.

```{r Remove short words}

@@

### Filtering and Casting

We summarise the data format into a more compressed form and convert it into a document term matrix.

```{r Term Frequency}

# Summarise
posts_tokenized.dt %>% 
  group_by(articleID, word) %>%
  dplyr::summarise(term_frequency = n()) %>%
  ungroup() ->
  posts_tokenized.dt

```{r Cast to DTM, eval=FALSE, include=FALSE}
# Convert to document term matrix
posts_tokenized.dt %>% 
  cast_dtm(articleID, word, term_frequency) ->
  posts_tokenized.dtm
```

@@

### Topic modelling

#### LDA Training

##### Build Corpus
```{r eval=FALSE, include=FALSE}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw

@@

##### Run LDA using Gibbs sampling

@@

```{r eval=FALSE, include=FALSE}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

@@

save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

Training took 50 minutes on the full dataset. We extract the word-topic probabilities, and the document-topic probabilities produced by the model.

alternatively...
```{r eval=FALSE, include=FALSE}
# Train the LDA model
LDA(
  x       = posts_tokenized.dtm,
  k       = 40,
  method  = "Gibbs",
  control = list(seed = 7292)
) -> posts.lda
```

@@

  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID) 
```
### Create Topic Labels
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

@@

We extract the top 30 most relevant words and plot them as follows:

  1. Compute the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities and construct a distance matrix,
  2. Apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
  3. Plot each word near the center of the topic mass and repel them from each other.

@@

set.seed(9272)
posts.dtp %>% 
  group_by(title = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw %>% select(title, articleID), by = "title") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>% 
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(10) %>% 
  mutate(row = row_number()) %>% 
  ungroup() ->
  posts_classification.sdt

>>>>

  library(tidytext)    # Tidy text mining
  library(tm)    # Tidy text mining
  library(hunspell)    # Text processing
  library(stringdist)  # String distances
  library(topicmodels) # Topic modelling
  library(stm)         # Sructural Topic Model
  library(proxy)       # Distance measures
  library(SnowballC)   # Stemming
})

```{r caching, echo = FALSE}
load("../output/models/LDAGibbs 40 .Rda")
#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE)

@@

![Research Strategy](../figs/research_strategy.png)

## Dataset

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6307 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from six different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the article. We include the month the document was written and the news agency as covariates on topical prevalence. We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.

We can see the number of articles by news agency and the how many of these articles were shared on Facebook on the following figure.

```{r echo=FALSE}
btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)

btw %>%
  ggplot(aes(site, fill=shared)) +
  geom_bar(alpha = .7) +
  labs(x="", y="Count") 
```

```{r include=FALSE}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") ->
  # Assign to variable
  posts_tokenized.dt

@@

# Summarise
posts_tokenized.dt %>% 
  group_by(articleID, word) %>%
  dplyr::summarise(term_frequency = n()) %>%
  ungroup() ->
  posts_tokenized.dt
```

@@

### LDA Training

```{r eval=FALSE, include=FALSE}
# Build Corpus
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw

@@

@@

```{r eval=FALSE, include=FALSE}
## Run LDA using Gibbs sampling

#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

@@

save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

@@

  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID) 
```

```{r message=FALSE, warning=FALSE}
### Create Topic Labels

## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

@@

### Sample articles

To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.

set.seed(9272)
posts.dtp %>% 
  group_by(title = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw %>% select(title, articleID), by = "title") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>% 
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(5, replace = TRUE) %>% 
  mutate(row = row_number()) %>% 
  ungroup() ->
  posts_classification.sdt

### News landscape

After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label. The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic. It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities. We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.

@@
